---
title: "R Notebook"
output: html_notebook
---

JMJPFU
28-Feb-2020
This is the notebook for exploratory data analysis for the Curn project. Lord bless this attempt of yours

# Let us look the first user record
```{r}
# Renaming the data frame
assign('churnData' ,`telecom_churn_data.(1)`)
```



```{r}
churnData[1:10,]
```


Let us look at the different columns and pick some of them for verification

```{r}
names(churnData)
```

# Find the columns with null values

```{r}
naData = data.frame(colSums(is.na(churnData)))
naData$percentage = (naData$colSums.is.na.churnData../nrow(churnData))*100
colnames(naData)[1] = c('NAs')
naData

```

# Derive summary statistics of various columns

```{r}
summary(churnData)
```

Let us find some columns where the column sums are zero. These columns have to be eliminated. To do that let us find those numeric columns

```{r}
library(dplyr)
numCols = churnData %>% select_if(is.numeric) %>% colnames()

numChurn = churnData[,numCols]
head(numChurn)
```

Now let us find those columns whose sums equal 0 and then find those column names

```{r}
#zeroCols = numChurn %>% colSums(na.rm = TRUE) %>% data.frame() %>% colnames('sum')
#zeroCols

zeroCols = colnames(numChurn[colSums(numChurn,na.rm = TRUE) == 0])

summary(numChurn[,zeroCols])
```

Lets eliminate these columns from the data set

```{r}
dim(numChurn)
# Removing the zero sum columns
numChurn <- numChurn %>% select(-c(zeroCols))

dim(numChurn)

```
```{r}
head(numChurn)
summary(numChurn)
```

Let us look at duplicates in the mobile number column 

```{r}
length(unique(numChurn$circle_id))
```


Let us now create the target variable which is the indicator for churn.

```{r}
# Consolidating the calls data for sept month
numChurn$SepCalls <- numChurn$total_ic_mou_9 + numChurn$total_og_mou_9

head(numChurn,n=10)
```

```{r}
# Consolidating the internet data for Sept month
numChurn$SepInternet <- numChurn$vol_2g_mb_9 + numChurn$vol_3g_mb_9

```

The customers who have no call and internet data in the Sept month would be the ones who have churned

```{r}
# First initialise all records to 0
numChurn$target <- 0

# Those rows where the calls and internet are zero is the churn data

numChurn[numChurn$SepCalls == 0 & numChurn$SepInternet == 0,'target'] <- 1

numChurn[0:50,203:206]
```

### Taking some variables and visualizing some trends with respect to Churn

Proposition 1 : Let us take the revenue per month for three months and take its standard deviation and then see if there are any trends coming up

```{r}
# take a sample of only the required variables
churnSamp1 <- numChurn %>% select(mobile_number,arpu_6,arpu_7,arpu_8,target)

# let us create a new sample to take only the ARPu figures to take row wise standard deviation

churnSamp2 <- churnSamp1 %>% select(arpu_6,arpu_7,arpu_8)

# Scaling the data

library(caret)

pp = preProcess(churnSamp2,method = 'scale')
churnSamp2_tran = predict(pp,churnSamp2)



```

```{r}
churnSamp2_tran <- transform(churnSamp2_tran,SD = apply(churnSamp2_tran,1,sd,na.rm = TRUE))

churnSamp2_tran

```

Let us add the mobile numbers to the data set and do some visuali


```{r}
churnSamp2_tran$mobile <- churnData$mobile_number
churnSamp2_tran$target <- numChurn$target
head(churnSamp2_tran)
```


Let us plot the standard deviation of the revenue and find some bins





```{r}
library(ggplot2)

churnSamp2_tran %>% ggplot(aes(mobile,SD)) + geom_point()

```

# The next task is to find the relationship between revenue and the possibility of churn. 

Hypothesis 1. 
Too much flux in the revenue can indicate propensity to churn

Let us look at cases where the standard deviation is above 5

```{r}
churnSamp2_tran %>% filter(SD > 5) %>% mutate(Per = sum(target)/n()) %>% select(Per) %>% summarise(Mn = mean(Per,na.rm = TRUE))



```
The number of customers who are likely to churn in the high sd range is almost 3 times the normal zone

Let us now look at the distribution of the sD


```{r}
churnSamp2_tran %>% ggplot(aes(x= SD)) + geom_density()

# Mapping the quantile values also
quantile(churnSamp2_tran$SD, c(.05, .15,.25,.5,.6,.75,.85, .98))

```
Let us plot some tables based on these bins and see the % of customers within these bins

```{r}
churnSamp2_tran %>% filter(SD < 0.05709328 ) %>% mutate(Per = sum(target)/n()) %>% select(Per) %>% summarise(NUm = n(),Mn = mean(Per,na.rm = TRUE))

churnSamp2_tran %>% filter(SD >= 0.05709328 & SD < 0.10041949  ) %>% mutate(Per = sum(target)/n()) %>% select(Per) %>% summarise(NUm = n(),Mn = mean(Per,na.rm = TRUE))

churnSamp2_tran %>% filter(SD >= 0.10041949 & SD < 0.13878567   ) %>% mutate(Per = sum(target)/n()) %>% select(Per) %>% summarise(NUm = n(),Mn = mean(Per,na.rm = TRUE))

churnSamp2_tran %>% filter(SD >= 0.13878567  & SD < 0.25155975   ) %>% mutate(Per = sum(target)/n()) %>% select(Per) %>% summarise(NUm = n(),Mn = mean(Per,na.rm = TRUE))

churnSamp2_tran %>% filter(SD >= 0.25155975  & SD < 0.31318986   ) %>% mutate(Per = sum(target)/n()) %>% select(Per) %>% summarise(NUm = n(),Mn = mean(Per,na.rm = TRUE))

churnSamp2_tran %>% filter(SD >= 0.31318986  & SD < 0.44807817   ) %>% mutate(Per = sum(target)/n()) %>% select(Per) %>% summarise(NUm = n(),Mn = mean(Per,na.rm = TRUE))

churnSamp2_tran %>% filter(SD >= 0.44807817  & SD < 0.61230192   ) %>% mutate(Per = sum(target)/n()) %>% select(Per) %>% summarise(NUm = n(),Mn = mean(Per,na.rm = TRUE))

churnSamp2_tran %>% filter(SD >= 0.61230192  & SD < 1.43997168    ) %>% mutate(Per = sum(target)/n()) %>% select(Per) %>% summarise(NUm = n(),Mn = mean(Per,na.rm = TRUE))

churnSamp2_tran %>% filter(SD >= 1.43997168) %>% mutate(Per = sum(target)/n()) %>% select(Per) %>% summarise(Mn = mean(Per,na.rm = TRUE),NUm = n())

```

# Feature Engineering 1 : 

Creating the standard deviation of the arpu accross months 6 to 8 seems to be a good indicator

```{r}
head(numChurn)
```

## Hypothesis 2:

Let us look at the on network mou. My hypothesis is there shouldnt be any change in the on network mou as to whether a customer is churning or not

```{r}
# take a sample of only the required variables
churnSamp1_hyp2 <- numChurn %>% select(mobile_number,offnet_mou_6,offnet_mou_7,offnet_mou_8,target)

# let us create a new sample to take only the ARPu figures to take row wise standard deviation

churnSamp2_hyp2 <- churnSamp1_hyp2 %>% select(offnet_mou_6,offnet_mou_7,offnet_mou_8)

churnSamp2_hyp2[is.na(churnSamp2_hyp2)] <- 0

# Scaling the data

library(caret)

pp = preProcess(churnSamp2_hyp2,method = 'scale')
churnSamp2_hyp2 = predict(pp,churnSamp2_hyp2)
churnSamp2_hyp2

```

```{r}
churnSamp2_hyp2 <- transform(churnSamp2_hyp2,SD = apply(churnSamp2_hyp2,1,sd,na.rm = TRUE))

churnSamp2_hyp2$mobile <- churnData$mobile_number
churnSamp2_hyp2$target <- numChurn$target
head(churnSamp2_hyp2)
```

```{r}
# Mapping the quantile values also
quantile(churnSamp2_hyp2$SD, c(.05, .15,.25,.5,.6,.75,.85, .95,.99))
```

```{r}
churnSamp2_hyp2 %>% filter(SD < 0.0007897178  ) %>% mutate(Per = sum(target)/n()) %>% select(Per) %>% summarise(NUm = n(),Mn = mean(Per,na.rm = TRUE))

churnSamp2_hyp2 %>% filter(SD >= 0.0007897178  & SD < 0.0099430038   ) %>% mutate(Per = sum(target)/n()) %>% select(Per) %>% summarise(NUm = n(),Mn = mean(Per,na.rm = TRUE))

churnSamp2_hyp2 %>% filter(SD >= 0.0099430038  & SD < 0.0207226499    ) %>% mutate(Per = sum(target)/n()) %>% select(Per) %>% summarise(NUm = n(),Mn = mean(Per,na.rm = TRUE))

churnSamp2_hyp2 %>% filter(SD >= 0.0207226499   & SD < 0.0641469656    ) %>% mutate(Per = sum(target)/n()) %>% select(Per) %>% summarise(NUm = n(),Mn = mean(Per,na.rm = TRUE))

churnSamp2_hyp2 %>% filter(SD >= 0.0641469656 & SD < 0.0966209515    ) %>% mutate(Per = sum(target)/n()) %>% select(Per) %>% summarise(NUm = n(),Mn = mean(Per,na.rm = TRUE))

churnSamp2_hyp2 %>% filter(SD >= 0.0966209515   & SD < 0.1959115512    ) %>% mutate(Per = sum(target)/n()) %>% select(Per) %>% summarise(NUm = n(),Mn = mean(Per,na.rm = TRUE))

churnSamp2_hyp2 %>% filter(SD >= 0.1959115512   & SD < 0.3696960453    ) %>% mutate(Per = sum(target)/n()) %>% select(Per) %>% summarise(NUm = n(),Mn = mean(Per,na.rm = TRUE))

churnSamp2_hyp2 %>% filter(SD >= 0.3696960453   & SD < 1.0014883183     ) %>% mutate(Per = sum(target)/n()) %>% select(Per) %>% summarise(NUm = n(),Mn = mean(Per,na.rm = TRUE))

churnSamp2_hyp2 %>% filter(SD >= 1.0014883183   & SD < 2.3819037846      ) %>% mutate(Per = sum(target)/n()) %>% select(Per) %>% summarise(NUm = n(),Mn = mean(Per,na.rm = TRUE))

churnSamp2_hyp2 %>% filter(SD >= 2.3819037846 ) %>% mutate(Per = sum(target)/n()) %>% select(Per) %>% summarise(Mn = mean(Per,na.rm = TRUE),NUm = n())
```

The behaviour with respect to network usage is found to be opposite of the behaviour which was found for average revenue.

Both the onnet and offnet usage behaviour has a parabolic relationship with churn.

### Let us look for other relationships

```{r}
churnData[1:10,]
```

Let u slook at roaming incoming and roaming outgoing relationships

Creating a function to do the job
```{r}



scalerFun <- function(var1,var2,var3){
  
 # take a sample of only the required variables
churnSamp1_hyp2 <- numChurn %>% select(mobile_number,var1,var2,var3)

# let us create a new sample to take only the ARPu figures to take row wise standard deviation

churnSamp2_hyp2 <- churnSamp1_hyp2 %>% select(var1,var2,var3)

churnSamp2_hyp2[is.na(churnSamp2_hyp2)] <- 0

# Scaling the data

pp = preProcess(churnSamp2_hyp2,method = 'scale')
churnSamp2_hyp2 = predict(pp,churnSamp2_hyp2)

churnSamp2_hyp2 <- transform(churnSamp2_hyp2,SD = apply(churnSamp2_hyp2,1,sd,na.rm = TRUE))

churnSamp2_hyp2$mobile <- churnData$mobile_number
churnSamp2_hyp2$target <- numChurn$target
churnSamp2_hyp2


# Quantile mapping

quantvals <- quantile(churnSamp2_hyp2$SD, c(.05, .15,.25,.5,.6,.75,.85, .95,.99),na.rm = TRUE)

val1 <- churnSamp2_hyp2 %>% filter(SD < quantvals[1]  ) %>% mutate(Per = sum(target)/n()) %>% select(Per) %>% summarise(NUm = n(),Mn = mean(Per,na.rm = TRUE))

val2 <-churnSamp2_hyp2 %>% filter(SD >= quantvals[1]  & SD < quantvals[2]   ) %>% mutate(Per = sum(target)/n()) %>% select(Per) %>% summarise(NUm = n(),Mn = mean(Per,na.rm = TRUE))

val3 <- churnSamp2_hyp2 %>% filter(SD >= quantvals[2]  & SD < quantvals[3]   ) %>% mutate(Per = sum(target)/n()) %>% select(Per) %>% summarise(NUm = n(),Mn = mean(Per,na.rm = TRUE))

val4 <-churnSamp2_hyp2 %>% filter(SD >= quantvals[3]   & SD < quantvals[4]   ) %>% mutate(Per = sum(target)/n()) %>% select(Per) %>% summarise(NUm = n(),Mn = mean(Per,na.rm = TRUE))

val5 <-churnSamp2_hyp2 %>% filter(SD >= quantvals[4] & SD < quantvals[5]    ) %>% mutate(Per = sum(target)/n()) %>% select(Per) %>% summarise(NUm = n(),Mn = mean(Per,na.rm = TRUE))

val6 <-churnSamp2_hyp2 %>% filter(SD >= quantvals[5]   & SD < quantvals[6]    ) %>% mutate(Per = sum(target)/n()) %>% select(Per) %>% summarise(NUm = n(),Mn = mean(Per,na.rm = TRUE))

val7 <-churnSamp2_hyp2 %>% filter(SD >= quantvals[6]   & SD < quantvals[7]    ) %>% mutate(Per = sum(target)/n()) %>% select(Per) %>% summarise(NUm = n(),Mn = mean(Per,na.rm = TRUE))

val8 <-churnSamp2_hyp2 %>% filter(SD >= quantvals[7]   & SD < quantvals[8]    ) %>% mutate(Per = sum(target)/n()) %>% select(Per) %>% summarise(NUm = n(),Mn = mean(Per,na.rm = TRUE))

val9 <-churnSamp2_hyp2 %>% filter(SD >= quantvals[8]   & SD < quantvals[9]      ) %>% mutate(Per = sum(target)/n()) %>% select(Per) %>% summarise(NUm = n(),Mn = mean(Per,na.rm = TRUE))

val10 <-churnSamp2_hyp2 %>% filter(SD >= quantvals[9] ) %>% mutate(Per = sum(target)/n()) %>% select(Per) %>% summarise(NUm = n(),Mn = mean(Per,na.rm = TRUE))

l1 = list(df1=churnSamp2_hyp2,val1=val1,val2=val2,val3=val3,val4=val4,val5=val5,val6=val6,val7=val7,val8=val8,val9=val9,val10=val10)

l1  

}


```

Running the function for roaming values

```{r}
roamSamp <- scalerFun('roam_ic_mou_6','roam_ic_mou_7','roam_ic_mou_8')
roamSamp$df1
roamSamp$val1
roamSamp$val2
roamSamp$val3
roamSamp$val4
roamSamp$val5
roamSamp$val6
roamSamp$val7
roamSamp$val8
roamSamp$val9
roamSamp$val10



```


## Result : Roaming. 
Roaming also is found to have the same behaviour as the other variables. The highest quantile values shows the maximum propensity to churn.

## Roaming Outgoing

```{r}
# make an empty data frame 

churnFeat1 <- data.frame(matrix( nrow = 99999, ncol = 0))


churnFeat1 <- cbind(churnFeat1,roamSamp$df1$SD)



colnames(churnFeat1) <- c('roam_ic_SD')

head(churnFeat1)

```




```{r}

roamSamp <- scalerFun('roam_og_mou_6','roam_og_mou_7','roam_og_mou_8')
roamSamp$df1
roamSamp$val1
roamSamp$val2
roamSamp$val3
roamSamp$val4
roamSamp$val5
roamSamp$val6
roamSamp$val7
roamSamp$val8
roamSamp$val9
roamSamp$val10

churnFeat1 <- cbind(churnFeat1,roamSamp$df1$SD)



colnames(churnFeat1) <- c('roam_ic_SD','roam_og_SD')

head(churnFeat1)

```

## Location outgoing same telecom provider

```{r}
roamSamp <- scalerFun('loc_og_t2t_mou_6','loc_og_t2t_mou_7','loc_og_t2t_mou_8')
roamSamp$df1
roamSamp$val1
roamSamp$val2
roamSamp$val3
roamSamp$val4
roamSamp$val5
roamSamp$val6
roamSamp$val7
roamSamp$val8
roamSamp$val9
roamSamp$val10

churnFeat1 <- cbind(churnFeat1,roamSamp$df1$SD)



colnames(churnFeat1) <- c('roam_ic_SD','roam_og_SD','loc_og_t2t_SD')

head(churnFeat1)

```

Local calls within the same network within the network of the same telecom operator shows a reverse trend where low flex zone has higher probability of finding churn cases.

## Local calls from operator to mobile of other operator


```{r}
roamSamp <- scalerFun('loc_og_t2m_mou_6','loc_og_t2m_mou_7','loc_og_t2m_mou_8')
roamSamp$df1
roamSamp$val1
roamSamp$val2
roamSamp$val3
roamSamp$val4
roamSamp$val5
roamSamp$val6
roamSamp$val7
roamSamp$val8
roamSamp$val9
roamSamp$val10

churnFeat1 <- cbind(churnFeat1,roamSamp$df1$SD)



colnames(churnFeat1) <- c('roam_ic_SD','roam_og_SD','loc_og_t2t_SD','loc_og_t2m_SD')

head(churnFeat1)
```

The proportion of the churn cases are more in the lower ranges of standard deviation

## Operator to fixed lines of the operator, outgoing

```{r}
roamSamp <- scalerFun('loc_og_t2f_mou_6','loc_og_t2f_mou_7','loc_og_t2f_mou_8')
roamSamp$df1
roamSamp$val1
roamSamp$val2
roamSamp$val3
roamSamp$val4
roamSamp$val5
roamSamp$val6
roamSamp$val7
roamSamp$val8
roamSamp$val9
roamSamp$val10

churnFeat1 <- cbind(churnFeat1,roamSamp$df1$SD)



colnames(churnFeat1) <- c('roam_ic_SD','roam_og_SD','loc_og_t2t_SD','loc_og_t2m_SD','loc_og_t2f_SD')

head(churnFeat1)

```

Not much information in this feature.

## Operator to its own call centre
Do calls to ones call centre indicate a propensity for churn ?

```{r}
roamSamp <- scalerFun('loc_og_t2c_mou_6','loc_og_t2c_mou_7','loc_og_t2c_mou_8')
roamSamp$df1
roamSamp$val1
roamSamp$val2
roamSamp$val3
roamSamp$val4
roamSamp$val5
roamSamp$val6
roamSamp$val7
roamSamp$val8
roamSamp$val9
roamSamp$val10

churnFeat1 <- cbind(churnFeat1,roamSamp$df1$SD)



colnames(churnFeat1) <- c('roam_ic_SD','roam_og_SD','loc_og_t2t_SD','loc_og_t2m_SD','loc_og_t2f_SD','loc_og_t2c_SD')

head(churnFeat1)

```
Not much information in this data point. 

## Local outgoing

```{r}
roamSamp <- scalerFun('loc_og_mou_6','loc_og_mou_7','loc_og_mou_8')
roamSamp$df1
roamSamp$val1
roamSamp$val2
roamSamp$val3
roamSamp$val4
roamSamp$val5
roamSamp$val6
roamSamp$val7
roamSamp$val8
roamSamp$val9
roamSamp$val10

churnFeat1 <- cbind(churnFeat1,roamSamp$df1$SD)



colnames(churnFeat1) <- c('roam_ic_SD','roam_og_SD','loc_og_t2t_SD','loc_og_t2m_SD','loc_og_t2f_SD','loc_og_t2c_SD','loc_og_SD')

head(churnFeat1)

```


Lower range of this has around 40% of churn cases.

## STD outgoing inter operator calls.

```{r}
roamSamp <- scalerFun('std_og_t2t_mou_6','std_og_t2t_mou_7','std_og_t2t_mou_8')
roamSamp$df1
roamSamp$val1
roamSamp$val2
roamSamp$val3
roamSamp$val4
roamSamp$val5
roamSamp$val6
roamSamp$val7
roamSamp$val8
roamSamp$val9
roamSamp$val10

churnFeat1 <- cbind(churnFeat1,roamSamp$df1$SD)



colnames(churnFeat1) <- c('roam_ic_SD','roam_og_SD','loc_og_t2t_SD','loc_og_t2m_SD','loc_og_t2f_SD','loc_og_t2c_SD','loc_og_SD','std_og_t2t_SD')

head(churnFeat1)

```


The higher end of the spectrum shows the highest propensity to churn.Top three bands of the standard deviation has the highest propensity.

## STD outgoing Operator to another operator mobile.

```{r}
roamSamp <- scalerFun('std_og_t2m_mou_6','std_og_t2m_mou_7','std_og_t2m_mou_8')
roamSamp$df1
roamSamp$val1
roamSamp$val2
roamSamp$val3
roamSamp$val4
roamSamp$val5
roamSamp$val6
roamSamp$val7
roamSamp$val8
roamSamp$val9
roamSamp$val10

churnFeat1 <- cbind(churnFeat1,roamSamp$df1$SD)



colnames(churnFeat1) <- c('roam_ic_SD','roam_og_SD','loc_og_t2t_SD','loc_og_t2m_SD','loc_og_t2f_SD','loc_og_t2c_SD','loc_og_SD','std_og_t2t_SD','std_og_t2m_SD')

head(churnFeat1)

```

The top end of the spectrum has the heighest propensity of churn.

## STD outgoing from same operator to fixed line

```{r}
roamSamp <- scalerFun('std_og_t2f_mou_6','std_og_t2f_mou_7','std_og_t2f_mou_8')
roamSamp$df1
roamSamp$val1
roamSamp$val2
roamSamp$val3
roamSamp$val4
roamSamp$val5
roamSamp$val6
roamSamp$val7
roamSamp$val8
roamSamp$val9
roamSamp$val10

churnFeat1 <- cbind(churnFeat1,roamSamp$df1$SD)



colnames(churnFeat1) <- c('roam_ic_SD','roam_og_SD','loc_og_t2t_SD','loc_og_t2m_SD','loc_og_t2f_SD','loc_og_t2c_SD','loc_og_SD','std_og_t2t_SD','std_og_t2m_SD','std_og_t2f_SD')

head(churnFeat1)

```

As expected the flux in fixed lines dosent present any meaningful indicator at all.

## STD outgoing consolidated

```{r}
roamSamp <- scalerFun('std_og_mou_6','std_og_mou_7','std_og_mou_8')
roamSamp$df1
roamSamp$val1
roamSamp$val2
roamSamp$val3
roamSamp$val4
roamSamp$val5
roamSamp$val6
roamSamp$val7
roamSamp$val8
roamSamp$val9
roamSamp$val10
churnFeat1 <- cbind(churnFeat1,roamSamp$df1$SD)



colnames(churnFeat1) <- c('roam_ic_SD','roam_og_SD','loc_og_t2t_SD','loc_og_t2m_SD','loc_og_t2f_SD','loc_og_t2c_SD','loc_og_SD','std_og_t2t_SD','std_og_t2m_SD','std_og_t2f_SD','std_og_SD')

head(churnFeat1)

```

There is a mild parabolic representation with the top standard deviation values having the higher probability of churn propensity.

## ISD outgoing

```{r}

roamSamp <- scalerFun('isd_og_mou_6','isd_og_mou_7','isd_og_mou_8')
roamSamp$df1
roamSamp$val1
roamSamp$val2
roamSamp$val3
roamSamp$val4
roamSamp$val5
roamSamp$val6
roamSamp$val7
roamSamp$val8
roamSamp$val9
roamSamp$val10

churnFeat1 <- cbind(churnFeat1,roamSamp$df1$SD)



colnames(churnFeat1) <- c('roam_ic_SD','roam_og_SD','loc_og_t2t_SD','loc_og_t2m_SD','loc_og_t2f_SD','loc_og_t2c_SD','loc_og_SD','std_og_t2t_SD','std_og_t2m_SD','std_og_t2f_SD','std_og_SD','isd_og_SD')

head(churnFeat1)

```

The highest band has the greatest probability of finding churn.

## Special outgoing calls

```{r}
roamSamp <- scalerFun('spl_og_mou_6','spl_og_mou_7','spl_og_mou_8')
roamSamp$df1
roamSamp$val1
roamSamp$val2
roamSamp$val3
roamSamp$val4
roamSamp$val5
roamSamp$val6
roamSamp$val7
roamSamp$val8
roamSamp$val9
roamSamp$val10

churnFeat1 <- cbind(churnFeat1,roamSamp$df1$SD)



colnames(churnFeat1) <- c('roam_ic_SD','roam_og_SD','loc_og_t2t_SD','loc_og_t2m_SD','loc_og_t2f_SD','loc_og_t2c_SD','loc_og_SD','std_og_t2t_SD','std_og_t2m_SD','std_og_t2f_SD','std_og_SD','isd_og_SD','spl_og_SD')

head(churnFeat1)

```


Not much difference in this segment.

## outgoing others

```{r}
roamSamp <- scalerFun('og_others_6','og_others_7','og_others_8')
roamSamp$df1
roamSamp$val1
roamSamp$val2
roamSamp$val3
roamSamp$val4
roamSamp$val5
roamSamp$val6
roamSamp$val7
roamSamp$val8
roamSamp$val9
roamSamp$val10

churnFeat1 <- cbind(churnFeat1,roamSamp$df1$SD)



colnames(churnFeat1) <- c('roam_ic_SD','roam_og_SD','loc_og_t2t_SD','loc_og_t2m_SD','loc_og_t2f_SD','loc_og_t2c_SD','loc_og_SD','std_og_t2t_SD','std_og_t2m_SD','std_og_t2f_SD','std_og_SD','isd_og_SD','spl_og_SD','og_others_SD')

head(churnFeat1)
```

The top one has the most propensity. However not much to talk about.

## Consolidate outgoing trend

```{r}
roamSamp <- scalerFun('total_og_mou_6','total_og_mou_7','total_og_mou_8')
roamSamp$df1
roamSamp$val1
roamSamp$val2
roamSamp$val3
roamSamp$val4
roamSamp$val5
roamSamp$val6
roamSamp$val7
roamSamp$val8
roamSamp$val9
roamSamp$val10

churnFeat1 <- cbind(churnFeat1,roamSamp$df1$SD)



colnames(churnFeat1) <- c('roam_ic_SD','roam_og_SD','loc_og_t2t_SD','loc_og_t2m_SD','loc_og_t2f_SD','loc_og_t2c_SD','loc_og_SD','std_og_t2t_SD','std_og_t2m_SD','std_og_t2f_SD','std_og_SD','isd_og_SD','spl_og_SD','og_others_SD','total_og_SD')

head(churnFeat1)

```

There is a parabolic relationsip. With some of the highest representation at the bottom end of the std range. The top also showing some propensity for the same. The bottom end must be heavily influenced by some of the 40% range features.

## Local incoming calls within the same telecom network

```{r}
roamSamp <- scalerFun('loc_ic_t2t_mou_6','loc_ic_t2t_mou_7','loc_ic_t2t_mou_8')
roamSamp$df1
roamSamp$val1
roamSamp$val2
roamSamp$val3
roamSamp$val4
roamSamp$val5
roamSamp$val6
roamSamp$val7
roamSamp$val8
roamSamp$val9
roamSamp$val10

churnFeat1 <- cbind(churnFeat1,roamSamp$df1$SD)



colnames(churnFeat1) <- c('roam_ic_SD','roam_og_SD','loc_og_t2t_SD','loc_og_t2m_SD','loc_og_t2f_SD','loc_og_t2c_SD','loc_og_SD','std_og_t2t_SD','std_og_t2m_SD','std_og_t2f_SD','std_og_SD','isd_og_SD','spl_og_SD','og_others_SD','total_og_SD','loc_ic_t2t_SD')

head(churnFeat1)

```
The bottom 15000 cases has the highest propensity for churn 24%

## Local incoming operator to different mobile network

```{r}
roamSamp <- scalerFun('loc_ic_t2m_mou_6','loc_ic_t2m_mou_7','loc_ic_t2m_mou_8')
roamSamp$df1
roamSamp$val1
roamSamp$val2
roamSamp$val3
roamSamp$val4
roamSamp$val5
roamSamp$val6
roamSamp$val7
roamSamp$val8
roamSamp$val9
roamSamp$val10

churnFeat1 <- cbind(churnFeat1,roamSamp$df1$SD)



colnames(churnFeat1) <- c('roam_ic_SD','roam_og_SD','loc_og_t2t_SD','loc_og_t2m_SD','loc_og_t2f_SD','loc_og_t2c_SD','loc_og_SD','std_og_t2t_SD','std_og_t2m_SD','std_og_t2f_SD','std_og_SD','isd_og_SD','spl_og_SD','og_others_SD','total_og_SD','loc_ic_t2t_SD','loc_ic_t2m_SD')

head(churnFeat1)

```

The bottom has a very high percentage of churn about 43%.

##Local incoming telecom operator to a fixed line

```{r}
roamSamp <- scalerFun('loc_ic_t2f_mou_6','loc_ic_t2f_mou_7','loc_ic_t2f_mou_8')
roamSamp$df1
roamSamp$val1
roamSamp$val2
roamSamp$val3
roamSamp$val4
roamSamp$val5
roamSamp$val6
roamSamp$val7
roamSamp$val8
roamSamp$val9
roamSamp$val10

churnFeat1 <- cbind(churnFeat1,roamSamp$df1$SD)



colnames(churnFeat1) <- c('roam_ic_SD','roam_og_SD','loc_og_t2t_SD','loc_og_t2m_SD','loc_og_t2f_SD','loc_og_t2c_SD','loc_og_SD','std_og_t2t_SD','std_og_t2m_SD','std_og_t2f_SD','std_og_SD','isd_og_SD','spl_og_SD','og_others_SD','total_og_SD','loc_ic_t2t_SD','loc_ic_t2m_SD','loc_ic_t2f_SD')

head(churnFeat1)

```

The bottom layer has the highest propensity for churn.

## Local Incoming 

```{r}
roamSamp <- scalerFun('loc_ic_mou_6','loc_ic_mou_7','loc_ic_mou_8')
roamSamp$df1
roamSamp$val1
roamSamp$val2
roamSamp$val3
roamSamp$val4
roamSamp$val5
roamSamp$val6
roamSamp$val7
roamSamp$val8
roamSamp$val9
roamSamp$val10
churnFeat1 <- cbind(churnFeat1,roamSamp$df1$SD)



colnames(churnFeat1) <- c('roam_ic_SD','roam_og_SD','loc_og_t2t_SD','loc_og_t2m_SD','loc_og_t2f_SD','loc_og_t2c_SD','loc_og_SD','std_og_t2t_SD','std_og_t2m_SD','std_og_t2f_SD','std_og_SD','isd_og_SD','spl_og_SD','og_others_SD','total_og_SD','loc_ic_t2t_SD','loc_ic_t2m_SD','loc_ic_t2f_SD','loc_ic_SD')

head(churnFeat1)
```

The bottom 5000 which has the least standard deviation has the higher proportion of churn with 42%.

## STD incoming within the same network

```{r}

roamSamp <- scalerFun('std_ic_t2t_mou_6','std_ic_t2t_mou_7','std_ic_t2t_mou_8')
roamSamp$df1
roamSamp$val1
roamSamp$val2
roamSamp$val3
roamSamp$val4
roamSamp$val5
roamSamp$val6
roamSamp$val7
roamSamp$val8
roamSamp$val9
roamSamp$val10

churnFeat1 <- cbind(churnFeat1,roamSamp$df1$SD)



colnames(churnFeat1) <- c('roam_ic_SD','roam_og_SD','loc_og_t2t_SD','loc_og_t2m_SD','loc_og_t2f_SD','loc_og_t2c_SD','loc_og_SD','std_og_t2t_SD','std_og_t2m_SD','std_og_t2f_SD','std_og_SD','isd_og_SD','spl_og_SD','og_others_SD','total_og_SD','loc_ic_t2t_SD','loc_ic_t2m_SD','loc_ic_t2f_SD','loc_ic_SD','std_ic_t2t_SD')

head(churnFeat1)

```

STD incoming dosent have much of a differentiation and the churn percentage is evenly distributed.

## STD incoming within network from mobile of other operator

```{r}
roamSamp <- scalerFun('std_ic_t2m_mou_6','std_ic_t2m_mou_7','std_ic_t2m_mou_8')
roamSamp$df1
roamSamp$val1
roamSamp$val2
roamSamp$val3
roamSamp$val4
roamSamp$val5
roamSamp$val6
roamSamp$val7
roamSamp$val8
roamSamp$val9
roamSamp$val10

roamSamp <- scalerFun('std_ic_t2t_mou_6','std_ic_t2t_mou_7','std_ic_t2t_mou_8')
roamSamp$df1
roamSamp$val1
roamSamp$val2
roamSamp$val3
roamSamp$val4
roamSamp$val5
roamSamp$val6
roamSamp$val7
roamSamp$val8
roamSamp$val9
roamSamp$val10

churnFeat1 <- cbind(churnFeat1,roamSamp$df1$SD)



colnames(churnFeat1) <- c('roam_ic_SD','roam_og_SD','loc_og_t2t_SD','loc_og_t2m_SD','loc_og_t2f_SD','loc_og_t2c_SD','loc_og_SD','std_og_t2t_SD','std_og_t2m_SD','std_og_t2f_SD','std_og_SD','isd_og_SD','spl_og_SD','og_others_SD','total_og_SD','loc_ic_t2t_SD','loc_ic_t2m_SD','loc_ic_t2f_SD','loc_ic_SD','std_ic_t2t_SD','std_ic_t2m_SD')

head(churnFeat1)

```

This is a parabolic distribution with the maximum propensity with the bottom band and high band. However the difference between bands is not that pronounced

## STD incoming from fixed line to the operator

```{r}
roamSamp <- scalerFun('std_ic_t2f_mou_6','std_ic_t2f_mou_7','std_ic_t2f_mou_8')
roamSamp$df1
roamSamp$val1
roamSamp$val2
roamSamp$val3
roamSamp$val4
roamSamp$val5
roamSamp$val6
roamSamp$val7
roamSamp$val8
roamSamp$val9
roamSamp$val10
churnFeat1 <- cbind(churnFeat1,roamSamp$df1$SD)



colnames(churnFeat1) <- c('roam_ic_SD','roam_og_SD','loc_og_t2t_SD','loc_og_t2m_SD','loc_og_t2f_SD','loc_og_t2c_SD','loc_og_SD','std_og_t2t_SD','std_og_t2m_SD','std_og_t2f_SD','std_og_SD','isd_og_SD','spl_og_SD','og_others_SD','total_og_SD','loc_ic_t2t_SD','loc_ic_t2m_SD','loc_ic_t2f_SD','loc_ic_SD','std_ic_t2t_SD','std_ic_t2m_SD','std_ic_t2f_SD')

head(churnFeat1)
```

Not much of differentiation

## Total STD incoming

```{r}
roamSamp <- scalerFun('std_ic_mou_6','std_ic_mou_7','std_ic_mou_8')
roamSamp$df1
roamSamp$val1
roamSamp$val2
roamSamp$val3
roamSamp$val4
roamSamp$val5
roamSamp$val6
roamSamp$val7
roamSamp$val8
roamSamp$val9
roamSamp$val10


churnFeat1 <- cbind(churnFeat1,roamSamp$df1$SD)

colnames(churnFeat1) <- c('roam_ic_SD','roam_og_SD','loc_og_t2t_SD','loc_og_t2m_SD','loc_og_t2f_SD','loc_og_t2c_SD','loc_og_SD','std_og_t2t_SD','std_og_t2m_SD','std_og_t2f_SD','std_og_SD','isd_og_SD','spl_og_SD','og_others_SD','total_og_SD','loc_ic_t2t_SD','loc_ic_t2m_SD','loc_ic_t2f_SD','loc_ic_SD','std_ic_t2t_SD','std_ic_t2m_SD','std_ic_t2f_SD','std_ic_SD')

head(churnFeat1)
```

A parabolic relationship with the bottom end having the maximum propensity of churn

## Total incoming calls 

```{r}
roamSamp <- scalerFun('total_ic_mou_6','total_ic_mou_7','total_ic_mou_8')
roamSamp$df1
roamSamp$val1
roamSamp$val2
roamSamp$val3
roamSamp$val4
roamSamp$val5
roamSamp$val6
roamSamp$val7
roamSamp$val8
roamSamp$val9
roamSamp$val10

churnFeat1 <- cbind(churnFeat1,roamSamp$df1$SD)

colnames(churnFeat1) <- c('roam_ic_SD','roam_og_SD','loc_og_t2t_SD','loc_og_t2m_SD','loc_og_t2f_SD','loc_og_t2c_SD','loc_og_SD','std_og_t2t_SD','std_og_t2m_SD','std_og_t2f_SD','std_og_SD','isd_og_SD','spl_og_SD','og_others_SD','total_og_SD','loc_ic_t2t_SD','loc_ic_t2m_SD','loc_ic_t2f_SD','loc_ic_SD','std_ic_t2t_SD','std_ic_t2m_SD','std_ic_t2f_SD','std_ic_SD','total_ic_SD')

head(churnFeat1)

```

For total incoming the bottom 5000 has the heighest % of churn cases with almost 40%. This could be on the basis of the feature with 43% churn percentage

## Special incoming

```{r}

roamSamp <- scalerFun('spl_ic_mou_6','spl_ic_mou_7','spl_ic_mou_8')
roamSamp$df1
roamSamp$val1
roamSamp$val2
roamSamp$val3
roamSamp$val4
roamSamp$val5
roamSamp$val6
roamSamp$val7
roamSamp$val8
roamSamp$val9
roamSamp$val10

churnFeat1 <- cbind(churnFeat1,roamSamp$df1$SD)

colnames(churnFeat1) <- c('roam_ic_SD','roam_og_SD','loc_og_t2t_SD','loc_og_t2m_SD','loc_og_t2f_SD','loc_og_t2c_SD','loc_og_SD','std_og_t2t_SD','std_og_t2m_SD','std_og_t2f_SD','std_og_SD','isd_og_SD','spl_og_SD','og_others_SD','total_og_SD','loc_ic_t2t_SD','loc_ic_t2m_SD','loc_ic_t2f_SD','loc_ic_SD','std_ic_t2t_SD','std_ic_t2m_SD','std_ic_t2f_SD','std_ic_SD','total_ic_SD','spl_ic_SD')

head(churnFeat1)


```
Nothing interesting going on here with the special calls.

##

```{r}
roamSamp <- scalerFun('isd_ic_mou_6','isd_ic_mou_7','isd_ic_mou_8')
roamSamp$df1
roamSamp$val1
roamSamp$val2
roamSamp$val3
roamSamp$val4
roamSamp$val5
roamSamp$val6
roamSamp$val7
roamSamp$val8
roamSamp$val9
roamSamp$val10

churnFeat1 <- cbind(churnFeat1,roamSamp$df1$SD)

colnames(churnFeat1) <- c('roam_ic_SD','roam_og_SD','loc_og_t2t_SD','loc_og_t2m_SD','loc_og_t2f_SD','loc_og_t2c_SD','loc_og_SD','std_og_t2t_SD','std_og_t2m_SD','std_og_t2f_SD','std_og_SD','isd_og_SD','spl_og_SD','og_others_SD','total_og_SD','loc_ic_t2t_SD','loc_ic_t2m_SD','loc_ic_t2f_SD','loc_ic_SD','std_ic_t2t_SD','std_ic_t2m_SD','std_ic_t2f_SD','std_ic_SD','total_ic_SD','spl_ic_SD','isd_ic_SD')

head(churnFeat1)

```

Nothing interesting going on here too

## Other incoming

```{r}
roamSamp <- scalerFun('ic_others_6','ic_others_7','ic_others_8')
roamSamp$df1
roamSamp$val1
roamSamp$val2
roamSamp$val3
roamSamp$val4
roamSamp$val5
roamSamp$val6
roamSamp$val7
roamSamp$val8
roamSamp$val9
roamSamp$val10

churnFeat1 <- cbind(churnFeat1,roamSamp$df1$SD)

colnames(churnFeat1) <- c('roam_ic_SD','roam_og_SD','loc_og_t2t_SD','loc_og_t2m_SD','loc_og_t2f_SD','loc_og_t2c_SD','loc_og_SD','std_og_t2t_SD','std_og_t2m_SD','std_og_t2f_SD','std_og_SD','isd_og_SD','spl_og_SD','og_others_SD','total_og_SD','loc_ic_t2t_SD','loc_ic_t2m_SD','loc_ic_t2f_SD','loc_ic_SD','std_ic_t2t_SD','std_ic_t2m_SD','std_ic_t2f_SD','std_ic_SD','total_ic_SD','spl_ic_SD','isd_ic_SD','ic_others_SD')

head(churnFeat1)

```

This is also not very promising feature

## Total recharge numbers

```{r}
roamSamp <- scalerFun('total_rech_num_6','total_rech_num_7','total_rech_num_8')
roamSamp$df1
roamSamp$val1
roamSamp$val2
roamSamp$val3
roamSamp$val4
roamSamp$val5
roamSamp$val6
roamSamp$val7
roamSamp$val8
roamSamp$val9
roamSamp$val10

churnFeat1 <- cbind(churnFeat1,roamSamp$df1$SD)

colnames(churnFeat1) <- c('roam_ic_SD','roam_og_SD','loc_og_t2t_SD','loc_og_t2m_SD','loc_og_t2f_SD','loc_og_t2c_SD','loc_og_SD','std_og_t2t_SD','std_og_t2m_SD','std_og_t2f_SD','std_og_SD','isd_og_SD','spl_og_SD','og_others_SD','total_og_SD','loc_ic_t2t_SD','loc_ic_t2m_SD','loc_ic_t2f_SD','loc_ic_SD','std_ic_t2t_SD','std_ic_t2m_SD','std_ic_t2f_SD','std_ic_SD','total_ic_SD','spl_ic_SD','isd_ic_SD','ic_others_SD','total_rech_num_SD')

head(churnFeat1)

```
The higher SD values have larger proportion of churn cases 26% compared to the other cases. 

## Total recharge amount

```{r}
roamSamp <- scalerFun('total_rech_amt_6','total_rech_amt_7','total_rech_amt_8')
roamSamp$df1
roamSamp$val1
roamSamp$val2
roamSamp$val3
roamSamp$val4
roamSamp$val5
roamSamp$val6
roamSamp$val7
roamSamp$val8
roamSamp$val9
roamSamp$val10
churnFeat1 <- cbind(churnFeat1,roamSamp$df1$SD)

colnames(churnFeat1) <- c('roam_ic_SD','roam_og_SD','loc_og_t2t_SD','loc_og_t2m_SD','loc_og_t2f_SD','loc_og_t2c_SD','loc_og_SD','std_og_t2t_SD','std_og_t2m_SD','std_og_t2f_SD','std_og_SD','isd_og_SD','spl_og_SD','og_others_SD','total_og_SD','loc_ic_t2t_SD','loc_ic_t2m_SD','loc_ic_t2f_SD','loc_ic_SD','std_ic_t2t_SD','std_ic_t2m_SD','std_ic_t2f_SD','std_ic_SD','total_ic_SD','spl_ic_SD','isd_ic_SD','ic_others_SD','total_rech_num_SD','total_rech_amt_SD')

head(churnFeat1)

```

The recharge amount has similar trend as recharge numbers

## maximum recharge amount

```{r}
roamSamp <- scalerFun('max_rech_amt_6','max_rech_amt_7','max_rech_amt_8')
roamSamp$df1
roamSamp$val1
roamSamp$val2
roamSamp$val3
roamSamp$val4
roamSamp$val5
roamSamp$val6
roamSamp$val7
roamSamp$val8
roamSamp$val9
roamSamp$val10

churnFeat1 <- cbind(churnFeat1,roamSamp$df1$SD)

colnames(churnFeat1) <- c('roam_ic_SD','roam_og_SD','loc_og_t2t_SD','loc_og_t2m_SD','loc_og_t2f_SD','loc_og_t2c_SD','loc_og_SD','std_og_t2t_SD','std_og_t2m_SD','std_og_t2f_SD','std_og_SD','isd_og_SD','spl_og_SD','og_others_SD','total_og_SD','loc_ic_t2t_SD','loc_ic_t2m_SD','loc_ic_t2f_SD','loc_ic_SD','std_ic_t2t_SD','std_ic_t2m_SD','std_ic_t2f_SD','std_ic_SD','total_ic_SD','spl_ic_SD','isd_ic_SD','ic_others_SD','total_rech_num_SD','total_rech_amt_SD','max_rech_amt_SD')

head(churnFeat1)

```

Not very pronounced trend here eventhough higher sd values band have higher percentage of churn cases.

## last day recharge amount

```{r}
roamSamp <- scalerFun('last_day_rch_amt_6','last_day_rch_amt_7','last_day_rch_amt_8')
roamSamp$df1
roamSamp$val1
roamSamp$val2
roamSamp$val3
roamSamp$val4
roamSamp$val5
roamSamp$val6
roamSamp$val7
roamSamp$val8
roamSamp$val9
roamSamp$val10

churnFeat1 <- cbind(churnFeat1,roamSamp$df1$SD)

colnames(churnFeat1) <- c('roam_ic_SD','roam_og_SD','loc_og_t2t_SD','loc_og_t2m_SD','loc_og_t2f_SD','loc_og_t2c_SD','loc_og_SD','std_og_t2t_SD','std_og_t2m_SD','std_og_t2f_SD','std_og_SD','isd_og_SD','spl_og_SD','og_others_SD','total_og_SD','loc_ic_t2t_SD','loc_ic_t2m_SD','loc_ic_t2f_SD','loc_ic_SD','std_ic_t2t_SD','std_ic_t2m_SD','std_ic_t2f_SD','std_ic_SD','total_ic_SD','spl_ic_SD','isd_ic_SD','ic_others_SD','total_rech_num_SD','total_rech_amt_SD','max_rech_amt_SD','last_day_rch_amt_SD')

head(churnFeat1)

```

Not a very informative feature

## Total recharge data

```{r}
roamSamp <- scalerFun('total_rech_data_6','total_rech_data_7','total_rech_data_8')
roamSamp$df1
roamSamp$val1
roamSamp$val2
roamSamp$val3
roamSamp$val4
roamSamp$val5
roamSamp$val6
roamSamp$val7
roamSamp$val8
roamSamp$val9
roamSamp$val10

churnFeat1 <- cbind(churnFeat1,roamSamp$df1$SD)

colnames(churnFeat1) <- c('roam_ic_SD','roam_og_SD','loc_og_t2t_SD','loc_og_t2m_SD','loc_og_t2f_SD','loc_og_t2c_SD','loc_og_SD','std_og_t2t_SD','std_og_t2m_SD','std_og_t2f_SD','std_og_SD','isd_og_SD','spl_og_SD','og_others_SD','total_og_SD','loc_ic_t2t_SD','loc_ic_t2m_SD','loc_ic_t2f_SD','loc_ic_SD','std_ic_t2t_SD','std_ic_t2m_SD','std_ic_t2f_SD','std_ic_SD','total_ic_SD','spl_ic_SD','isd_ic_SD','ic_others_SD','total_rech_num_SD','total_rech_amt_SD','max_rech_amt_SD','last_day_rch_amt_SD','total_rech_data_SD')

head(churnFeat1)


```
Not much informative features

## Maximum recharge for data

```{r}
roamSamp <- scalerFun('max_rech_data_6','max_rech_data_7','max_rech_data_8')
roamSamp$df1
roamSamp$val1
roamSamp$val2
roamSamp$val3
roamSamp$val4
roamSamp$val5
roamSamp$val6
roamSamp$val7
roamSamp$val8
roamSamp$val9
roamSamp$val10

churnFeat1 <- cbind(churnFeat1,roamSamp$df1$SD)

colnames(churnFeat1) <- c('roam_ic_SD','roam_og_SD','loc_og_t2t_SD','loc_og_t2m_SD','loc_og_t2f_SD','loc_og_t2c_SD','loc_og_SD','std_og_t2t_SD','std_og_t2m_SD','std_og_t2f_SD','std_og_SD','isd_og_SD','spl_og_SD','og_others_SD','total_og_SD','loc_ic_t2t_SD','loc_ic_t2m_SD','loc_ic_t2f_SD','loc_ic_SD','std_ic_t2t_SD','std_ic_t2m_SD','std_ic_t2f_SD','std_ic_SD','total_ic_SD','spl_ic_SD','isd_ic_SD','ic_others_SD','total_rech_num_SD','total_rech_amt_SD','max_rech_amt_SD','last_day_rch_amt_SD','total_rech_data_SD','max_rech_data_SD')

head(churnFeat1)


```

This strategy of standard deviation not very informative for these features

## Count of 2g /3g recharge

```{r}
roamSamp <- scalerFun('jun_vbc_3g','jul_vbc_3g','aug_vbc_3g')
roamSamp$df1
roamSamp$val1
roamSamp$val2
roamSamp$val3
roamSamp$val4
roamSamp$val5
roamSamp$val6
roamSamp$val7
roamSamp$val8
roamSamp$val9
roamSamp$val10

churnFeat1 <- cbind(churnFeat1,roamSamp$df1$SD)

colnames(churnFeat1) <- c('roam_ic_SD','roam_og_SD','loc_og_t2t_SD','loc_og_t2m_SD','loc_og_t2f_SD','loc_og_t2c_SD','loc_og_SD','std_og_t2t_SD','std_og_t2m_SD','std_og_t2f_SD','std_og_SD','isd_og_SD','spl_og_SD','og_others_SD','total_og_SD','loc_ic_t2t_SD','loc_ic_t2m_SD','loc_ic_t2f_SD','loc_ic_SD','std_ic_t2t_SD','std_ic_t2m_SD','std_ic_t2f_SD','std_ic_SD','total_ic_SD','spl_ic_SD','isd_ic_SD','ic_others_SD','total_rech_num_SD','total_rech_amt_SD','max_rech_amt_SD','last_day_rch_amt_SD','total_rech_data_SD','max_rech_data_SD','aug_vbc_SD')

head(churnFeat1)

```


count_rech_2g_6 : Not informative 
count_rech_3g_6 : Not informative 
av_rech_amt_data_6
vol_2g_mb_6 / 3g
arpu_3g_8 / 2g
night_pck_user_8










```{r}
churnData[1:10,]
```




## Using the new features to build a model

```{r}


# Adding the target variable with the new features

churnFeat1$churn <- churnSamp2_tran$target
head(churnFeat1)

```
# Let us spot check with different models

```{r}
library(caret)

churnFeat1$churn <- factor(churnFeat1$churn)

# 10 fold cross validation

trainC <- trainControl(method='repeatedcv',number = 10,repeats = 3,classProbs = FALSE)

metric  <- 'Accuracy'

# Logistic Regression

set.seed(123)

fit.glm <- train(churn~.,data = churnFeat1,method='glm',metric='Accuracy',trControl=trainC)

# GLMNET

set.seed(123)

fit.glmnet <- train(churn~.,data = churnFeat1,method='glmnet',metric=metric,trControl=trainC)

# KNN

set.seed(123)

fit.knn <- train(churn~.,data = churnFeat1,method='knn',metric=metric,trControl=trainC)

# CART

set.seed(123)

fit.cart <- train(churn~.,data = churnFeat1,method='rpart',metric=metric,trControl=trainC)

# NB

set.seed(123)

fit.nb <- train(churn~.,data = churnFeat1,method='nb',metric=metric,trControl=trainC)

# SVM

set.seed(123)

fit.svm <- train(churn~.,data = churnFeat1,method='svmRadial',metric=metric,trControl=trainC)

# Bagged CART

set.seed(123)

fit.treebag <- train(churn~.,data = churnFeat1,method='treebag',metric=metric,trControl=trainC)

# RF

set.seed(123)

fit.RF <- train(churn~.,data = churnFeat1,method='rf',metric=metric,trControl=trainC)

# Stochastic Gradient boosting

set.seed(123)

fit.gbm <- train(churn~.,data = churnFeat1,method='gbm',metric=metric,trControl=trainC,verbose=FALSE)


# Comparing algorithms

results <- resamples(list(LG=fit.glm,Glmnet=fit.glmnet,KNN = fit.knn,CART=fit.cart,NB=fit.nb,BCART=fit.treebag,RF = fit.RF,GBM=fit.gbm))

summary(results)

dotPlot(results)


```

```{r}
unique(churnFeat1$churn)
```

# Let us look at a benchmark model and check its accuracy rates

```{r}
head(numChurn)
```

Let us remove some unwanted columns and then prepare a train and test sets

# List of columns where we impute zero in place of null values

```{r}
zero_impute = c('total_rech_data_6', 'total_rech_data_7', 'total_rech_data_8', 'total_rech_data_9',
        'av_rech_amt_data_6', 'av_rech_amt_data_7', 'av_rech_amt_data_8', 'av_rech_amt_data_9',
        'max_rech_data_6', 'max_rech_data_7', 'max_rech_data_8', 'max_rech_data_9')

# Imputing the rows with na values with zero

numChurn[is.na(numChurn),zero_impute] <- 0
       
```
```{r}
samp1 <- numChurn[,zero_impute]

nrow(samp1)

samp1[is.na(samp1),] <- 0 
  
  
  